%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Quantum Software Engineering Lead (Intern)} 
    {Qualcomm Institute} 
    {La Jolla, California} 
    {Jul. 2022 - Dec. 2024} 
    {
      \begin{cvitems}
        \item {Architected a quantum-encrypted video platform via photonic circuitry, achieving secure key distribution at \qiQubitCount{} qubits with <\qiQBER\% QBER over \qiChannelDistance{}-meter channels.}
        \item {Optimized Grover's algorithm in Qiskit for binary constraint satisfaction, achieving \groverSpeedup{}x speedup over classical brute-force on \groverVariables{}-variable problems with \groverDepthReduction\% circuit depth reduction.}
        \item {Built and benchmarked QML classification models via quantum neural networks, achieving \qmlAccuracy\% accuracy on \qmlDataset{}, outperforming classical baselines by \qmlBaselineGain{} percentage points.}
        \item {Mentored a cross-functional team of \qiInternCount{} interns under Dr.\ Nikola Alic, overseeing software deliverables and commissioning a new undergraduate quantum computing lab.}
      \end{cvitems}
    }
    
  \cventry
    {Full-Stack DevOps Engineer \& Advisor} 
    {Rochester Institute of Technology Esports} 
    {Remote (Rochester, New York)} 
    {Sep. 2020 - Jul. 2022} 
    {
      \begin{cvitems}
        \item {Engineered and deployed MERN-stack web resources via Docker, serving \ritMAU{} monthly active users across \ritTeamCount{} varsity esports teams.}
        \item{Orchestrated cloud infrastructure on DigitalOcean Droplets, implementing Nginx reverse proxies and Docker Compose to ensure 99.9\% uptime for high-traffic services.}
        \item{Built CI/CD pipelines and monitoring suites, reducing deployment time from \ritDeployBefore{} hours (manual) to \ritDeployAfter{} minutes and saving \textasciitilde\ritHoursSaved{} hours/year in release effort.}
      \end{cvitems}
    }

  \cventry
    {Instructor \& IT Systems Specialist} 
    {Mathnasium} 
    {Temecula, California} 
    {Mar. 2020 - Sep. 2021} 
    {
      \begin{cvitems} 
        \item {Delivered advanced technical instruction in Calculus and Computer Science, tailoring complex concepts to diverse student learning levels.}
        \item {Directed the center's digital transformation during COVID-19, authoring technical documentation and maintaining IT infrastructure to enable seamless remote learning.}
      \end{cvitems}
    }

\end{cventries}