%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& President (2023 - 2024)\& Technical Curriculum Lead} 
    {Quantum Computing at UC San Diego} 
    {La Jolla, CA} 
    {Feb. 2021 - Dec. 2024} 
    {
      \begin{cvitems} 
        \item {Co-founded and scaled the first undergraduate quantum computing organization at UC San Diego, establishing a community for 100+ aspiring researchers and engineers.}
        \item {Developed a technical curriculum spanning \qcWorkshopsPerQtr{} quarterly workshops, educating \qcStudentsEducated{} students with average attendance growing from \qcAttendanceStart{} to \qcAttendanceEnd{}.}
        \item {Standardized organizational workflows and digital infrastructure, enabling sustainable leadership transitions and cross-campus collaborations.}
        \item {Presented components of internship to organization members, including quantum-encrypted communication and quantum search algorithms.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {President \& Cybersecurity Competition Member} 
    {ACM Cyber @ UCSD} 
    {La Jolla, California} 
    {Aug 2020 - June 2023} 
    {
      \begin{cvitems} 
        \item {Trained teams for (and competed in) high-stakes national and international competitions including CCDC, CPTC, and Google CTF.}
        \item {Authored pedagogical training modules on penetration testing, network defense, and cryptography to elevate the club's competitive ranking.}
        \item {Orchestrated weekly technical workshops and "Deep Dive" sessions, fostering a culture of peer-to-peer mentorship in advanced security topics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Infrastructure Engineer \& Challenge Designer} 
    {San Diego Capture the Flag (SDCTF)} 
    {Remote} 
    {Dec. 2020 - May 2022} 
    {
      \begin{cvitems}
          \item{Engineered the backend for San Diego's largest annual cybersecurity competition, supporting 500+ global participants in its inaugural year.}
          \item {Provisioned cloud-native infrastructure using Terraform (IaC), managing a Postgres database and containerized challenge environments.}
          \item {Designed and deployed a Discord.JS-integrated submission bot to automate real-time flag validation and leaderboard updates.}
          \item {Developed high-quality Open Source Intelligence (OSINT) challenges, testing competitors' ability to perform investigative digital forensics.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}